Command line programs from LatticeRepLib

### 2023-01-12 ProgramSummary/ProgramSummary..tex
updating CmdPath writeup

		\begin{longtable}{l l l p{.2\textwidth} p{.5\textwidth} l}
			\caption{Summary of programs manipulating data}
			\label{processingprogs}\\ %NOTE: that lineskip is necessary to prevent toprule from crashing
			\toprule
			Name		&	in	&	out		&	\begin{parbox}[t]{2cm}{
				command line\\
				param{s}}
			\end{parbox}	& Output	\\
			\midrule
			CmdCmplx	&	NA	&	y		&\hrulefill	&Currently, 
				this just outputs some programmed examples.		\\[.9pt]
			CmdDelone	&	y	&	\SVI{}	&\hrulefill	&Converts input to \SVI{}		\\[.9pt]
			CmdGen		&	NA	&	\GVI{}	&	ngen - number of examples to generate (optional)\\
				{}		&		&			&type		& - lattice type to 
				generate, many options (optional) 
				c,t,h,o,r,h,m,a, 
				cP, cF,cI, tP, tI, hP, hR, oP, oF, oI, oS, mP, mC, mS, aP, 
				numeric Niggli types - 1-44, 
				Delone types - C1,C3,C5,~\dots 
				If no parameters are present, one each of the 44 Niggli types. 
				If only a number is present, that is how many of each of the 44 Niggli types to generate.
				For usage examples, see Table \ref{CMDGENexamples}\\[.9pt]
			CmdLM		&	y	&	y		&	\hrulefill		&		Lattice Matching. 
				The first input cell is used as the reference. 
				Succeeding cells are matched 
				as well as possible to the reference cell.\\[.9pt]
			CmdNiggli	&	y	&	\GVI{}	&\hrulefill	&		
				Produces the Niggli reduced cell for 	each input\\[.9pt]
			CmdPath		&	y	& \SVI{}			&
			no. of points	& If the number of points is 
			not used on the command line, the default number to generate is 20.		\\[.9pt]
			CmdPerturb	&	y	& y			&	n-number of perturbations,

>>>>

		\begin{longtable}{l l l p{.2\textwidth} p{.5\textwidth} l}
			\caption{Summary of programs manipulating data}
			\label{processingprogs}\\ %NOTE: that lineskip is necessary to prevent toprule from crashing
			\toprule
			Name		&	in	&	out		&	\begin{parbox}[t]{2cm}{
				command line\\
				param{s}}
			\end{parbox}	& Output	\\
			\midrule
			CmdCmplx	&	NA	&	y		&\hrulefill	&Currently, 
				this just outputs some programmed examples.		\\[.9pt]
			CmdDelone	&	y	&	\SVI{}	&\hrulefill	&Converts input to \SVI{}		\\[.9pt]
			CmdGen		&	NA	&	\GVI{}	&	ngen - number of examples to generate (optional)\\
				{}		&		&			&type		& - lattice type to 
				generate, many options (optional) 
				c,t,h,o,r,h,m,a, 
				cP, cF,cI, tP, tI, hP, hR, oP, oF, oI, oS, mP, mC, mS, aP, 
				numeric Niggli types - 1-44, 
				Delone types - C1,C3,C5,~\dots 
				If no parameters are present, one each of the 44 Niggli types. 
				If only a number is present, that is how many of each of the 44 Niggli types to generate.
				For usage examples, see Table \ref{CMDGENexamples}\\[.9pt]
			CmdLM		&	y	&	y		&	\hrulefill		&		Lattice Matching. 
				The first input cell is used as the reference. 
				Succeeding cells are matched 
				as well as possible to the reference cell.\\[.9pt]
			CmdNiggli	&	y	&	\GVI{}	&\hrulefill	&		
				Produces the Niggli reduced cell for 	each input\\[.9pt]
			CmdPath		&	y	& \SVI{}			&
			no. of points	& If the number of points is 
			not on the command line, the default number 
			to generate is 20.	If there is only one point, 
			then the second point is generated as the 
			Niggli reduced cell. If more than two points are input, 
			each successive pair will
			generate a list of output points; so if
			3 cells are input, the output will be 
			2 times the number of points requested.	\\[.9pt]
			CmdPerturb	&	y	& y			&	n-number of perturbations,
